Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-19 prop_letter.tex
prop_letter.tex Easy updates after the meeting...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kochen-Specker} 
\label{sec:Kochen-Specker}

@@

\section{Gleason}

@@

\noindent Because of the similarity between Def.~\ref{def:THOS}
and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
no matter in classical or quantum case. Conversely, if $\iota\circ\mu$
is always a IVPM, then $\iota$ must be a THOS rule.

@@

Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
may still be a QIVPM under some suitable conditions. For example,
Eq.~(\ref{eq:iota-Inclusion}) can be weaken as follow: for any numbers~$x_{0}$
and $x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.

@@

\begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals $\delta$. Given any state~$\rho$,
if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kochen-Specker Theorem and Contextuality}
\label{sec:Kochen-Specker}

@@

\section{Gleason's Theorem and Born rule}

@@

\noindent Because Eqs.~(\ref{eq:iota-constraints}) are the direct
counterpart of Eqs.~(\ref{eq:QIVPM-constraints}) and Eq.~(\ref{eq:iota-Inclusion})
is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
and Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
$\iota\circ\mu$ should always be a IVPM no matter in classical or
quantum case. Conversely, if $\iota\circ\mu$ is always a IVPM, then
$\iota$ must be a THOS rule. In other words, $\iota$ is a THOS rule
is a necessary and sufficient condition for $\iota\circ\mu$ is always
a IVPM as we next show.

@@

@@

\begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals $\delta$. Given any state~$\rho$,
if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}

@@

Even if a THOS rule~$\iota$ maps to $\mathscr{I}_{0}$ or infinite
intervals, the composited function~$\iota\circ\mu$ mapping to a
finite set of intervals~$\mathscr{I}$ may still be a QIVPM when
$\iota$ is not a THOS rule. For example, we can weaken Eq.~(\ref{eq:iota-Inclusion})
to the following condition: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
More concretely, given a three-dimensional Hilbert space, consider
two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$,
and a interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
\begin{equation}
\iota_{2}\left(x\right)=\begin{cases}
\imposs\,, & \textrm{ if }x=0\,;\\
\left[0,\tfrac{1}{4}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{8}\right]\,;\\
\left[0,{\textstyle \tfrac{1}{2}}\right]\,, & \textrm{ if }x\in\left(\tfrac{1}{8},\tfrac{3}{8}\right)\,;\\
\left[\tfrac{1}{4},\tfrac{3}{4}\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{8},\tfrac{5}{8}\right]\,;\\
\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left(\tfrac{5}{8},\tfrac{7}{8}\right)\,;\\
\left[\tfrac{1}{4},1\right]\,, & \textrm{ if }x\in\left[\tfrac{7}{8},1\right)\,;\\
\necess\,, & \textrm{ if }x=1\,.
\end{cases}\label{eq:iota}
\end{equation}
Since $\iota_{2}$ satisfies Eqs.~(\ref{eq:iota-constraints}) and
Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are a QIVPMs. By
Thm.~\ref{thm:Finite-precision-Gleason}, $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$.
This is true because the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
is $\frac{1}{24}$.
